\textit{Supplementary Material} \\ Predicting Solid State Material Platforms for Quantum Technologies

### 2022-03-08 supplementary.tex
Updates from Overleaf

Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training, test and validation sets derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$. All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional. Note that materials can appear several times in the list due  to  different  structures of the same composition. The  list  contains $5$ elementary (unary), $46$ binary and  $15$ ternary compounds.

>>>>

Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training and test sets derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$. All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional. Note that materials can appear several times in the list due  to  different  structures of the same composition. The  list  contains $5$ elementary (unary), $46$ binary and  $15$ ternary compounds.
